Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-07-13 tex/scam/abstract.tex
typo

\begin{abstract}
  We study the problem of variable selection in convex nonparametric
  regression.  Under the assumption that the true regression function
  is convex and sparse, we develop a screening procedure to select a
  subset of variables that contains the relevant variables. Our
  approach is a two-stage quadratic programming method that estimates
  a sum of one-dimensional convex functions, followed by
  one-dimensional concave regression fits on the residuals.  In
  contrast to previous methods for sparse additive models, the
  optimization is finite dimensional and requires no tuning parameters
  for smoothness. Under appropriate assumptions, we prove that the
  procedure is faithful in the population setting, yielding no false
  negatives.  We give a finite sample statistical analysis, and introduce
  algorithms for efficiently carrying out the required quadratic
  programs. The approach leads to significant computational and
  statistical advantages over fitting a full model, and provides an
  effective, practical approach to variable screening in convex
  regression.
\end{abstract}

>>>>

\begin{abstract}
  We study the problem of variable selection in convex nonparametric
  regression.  Under the assumption that the true regression function
  is convex and sparse, we develop a screening procedure to select a
  subset of variables that contains the relevant variables. Our
  approach is a two-stage quadratic programming method that estimates
  a sum of one-dimensional convex functions, followed by
  one-dimensional concave regression fits on the residuals.  In
  contrast to previous methods for sparse additive models, the
  optimization is finite dimensional and requires no tuning parameters
  for smoothness. Under appropriate assumptions, we prove that the
  procedure is faithful in the population setting, yielding no false
  negatives.  We give a finite sample statistical analysis, and
  introduce algorithms for efficiently carrying out the required
  quadratic programs. The approach leads to computational and
  statistical advantages over fitting a full model, and provides an
  effective, practical approach to variable screening in convex
  regression.
\end{abstract}
